Share Buyback and Equity Issue Anomalies Revisited

### 2016-02-24 report.Rnw
tool

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('report.Rnw', texi2dvi='texi2dvi'); file.remove(paste("report",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#Timing: 
require(tictoc)
tic() #without report_tool.R: 77s

###################################################
## SAME AS bb_issuers.Rnw
reload_data = 1

@@

source("lib_helpers.R")
source("latex_code.R")
source("dataset/indices_and_factors/ff_industries_sic.R")
source("business_data_clean.R")
source("Paper_global_parameters.R")

if (generate_rnw_data == 1){
  source("bb_issuers.R")
}  else{
  if (reload_data)
    #load("tmpfiles/bb_issuersALL.Rdata")
    load("bb_issuersTOOL.Rdata")
  source("lib_helpers.R") 
  source("latex_code.R")
  source("dataset/indices_and_factors/ff_industries_sic.R")
  source("business_data_clean.R")
  source("Paper_global_parameters.R")
}

@@

#Add any/all choices made in the tool here
if(!exists("input")){
  input = list()
  input$startdate <- as.Date("2000-12-31")
  input$enddate <- as.Date("2014-12-31")
  input$market_cap_min = 50
  input$market_cap_max = 505755
  input$quantile_used_ind = 0.2
  input$quantile_used_all = 0.4

@@

  input$characteristic_irats2 <- "Pre.Vol.Score"
  input$characteristic_irats2_sign <- T
}

options(warn=-1) #because some period don't have data
source("report_helpers.R")
source("report_tool.R")
source("report_tool_section.R")
options(warn=0)

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of share authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
SEO_exit_days = sapply(which(BUYBACK_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])
@

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
tmp = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
ri = remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)
expost_betas = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
ri = remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_12M,min_date=FirstTrade)
expost_betas_unhedged = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
@

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all1mshort_risk_factors,min_date=FirstTrade))
months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all3mshort_risk_factors,min_date=FirstTrade))
months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all6mshort_risk_factors,min_date=FirstTrade))
months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))
months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all24mshort_risk_factors,min_date=FirstTrade))
months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all36mshort_risk_factors,min_date=FirstTrade))
months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$long_all48mshort_risk_factors,min_date=FirstTrade))

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
Under_IdioBB_cor = cor(EU_index_features)
@

@@

Figure~\ref{fig:Eundervaluationindex} shows the distribution of the EU-index. The index has a symmetric distribution with a mean of \Sexpr{round(mean(EUindex_bb),2)}. Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics. Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}. Debt is the sum of the Compustat variables $dlc+ dltt$, where $dlc$ is ``Debt in Current Liabilities'' and $dltt$ is ``Long Term Debt - Total''. Equity is the Compustat variable $seq$ which is ``Total Parent Stockholders' Equity''. We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above. Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}. ``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp_market_cap = round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
@

First there is a striking negative relation between the EU index and financial leverage. This makes sense according to the static trade-off theory of optimal capital structure: high risky firms have more financial distress and should have less debt. Second, the high EU index firms are more likely to miss earnings forecasts. To the extent that analysts base their recommendations on these earnings misses, stock prices may become undervalued. Evidence that analyst extrapolation forecast errors are a partial explanation for the buyback anomaly is documented by \cite{PeyerVermaelen2009}.  High EU index firms are more likely to mention ``undervaluation'' as a motivation for the buyback.  High EU index firms tend to have more cash. This could of course be related to the fact that risky firms should have more cash holdings.  They also tend to follow up with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business. The table also shows a strong negative relation between market-to-book ratios and market capitalization and the EU index, which is not surprising as these are components of the index. It should be noted that the EU 6 portfolio is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million. The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.3$\%$ (i.e. portfolios EU4 through EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} billion (not indicated in the Table). So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
tmp = pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade))
tmp1 = pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade))

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(BUYBACK_DATA$long_all12mshort_risk_factors,min_date=FirstTrade)), 
  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:allhedgedBB", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

@@

number_eventsBB = table(format(BUYBACK_DATA$DATASET$SDC$Event.Date[BUYBACK_DATA$DATASET$SDC$Event.Date >= FirstTrade], "%Y"))
market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
market_index = market_index[which(str_sub(names(market_index), start = 6, end = 7)=="12")]
names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
df.bar <- barplot(number_eventsBB,col=c("grey"),main = "Panel A: Buyback Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.6)
par(new = TRUE)
plot(market_index,type="l", lwd = 1.5, axes = FALSE, xlab = "", ylab = "")
points(market_index, pch=1,  lwd=1.5)
axis(side=4, at = pretty(range(market_index)))
mtext("Market Index", side=4, line=3)
for (iter in 1:floor(max(number_eventsBB)/100))
  abline(h = 100*iter)

@@

all_ret_values = data.frame(
  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade)), start = 1, end = 7)]),
  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade))]),
  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_1M,min_date=FirstTrade)),
  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_3M,min_date=FirstTrade)),
  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_6M,min_date=FirstTrade)),
  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_12M,min_date=FirstTrade)),
  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_24M,min_date=FirstTrade)),
  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_36M,min_date=FirstTrade)),
  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA$pnl_returns_events_all_48M,min_date=FirstTrade))
)
plot(all_ret_values$market, axes=FALSE, ylab="Cumulative Returns", xlab = "Time",ylim=c(min(as.vector(all_ret_values)), max(as.vector(all_ret_values))), main = "Panel A: Absolute Returns", cex.lab=1.1, lty = "dotdash", type = "l", lwd=2)
axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(all_ret_values$months1, lty="solid", lwd=2)
lines(all_ret_values$months3, lty="dashed", lwd=2)
lines(all_ret_values$months6, lty="dotted", lwd=3)
lines(all_ret_values$months12, lty="dotted", lwd=2.5)
lines(all_ret_values$months24, lty="dotted", lwd=2)
lines(all_ret_values$months36, lty="dotted", lwd=1.5)
lines(all_ret_values$months48, lty="dotted", lwd=1)
for (iter in 1:floor(max(as.vector(all_ret_values))/100))
  abline(h = 100*iter)
#plot_crisis_dates(all_ret_values)
legend(x="topleft",
       c("S&P500","1 Month","3 Months","12 Months","24 Months","36 Months","48 Months"),
       lty=c("dotdash","solid","dashed","dotted","dotted","dotted","dotted","dotted"),
       lwd=c(2,2,2,3,2.5,2,1.5,1),
       cex=1,bg="white",inset=0.01)

>>>>

<< Data loading and recalculation, eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('report.Rnw', texi2dvi='texi2dvi'); file.remove(paste("report",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#Timing: 
require(tictoc)
tic() #without report_tool.R: 77s
###################################################
## SAME AS bb_issuers.Rnw
reload_data = 1

@@

source("lib_helpers.R",local=environment())
source("latex_code.R",local=environment())
source("dataset/indices_and_factors/ff_industries_sic.R",local=environment())
source("business_data_clean.R",local=environment())
source("Paper_global_parameters.R",local=environment())

if (generate_rnw_data == 1){
  source("bb_issuers.R",local=environment())
}  else{
  if (reload_data)
    load(normalizePath("bb_issuersTOOL.Rdata"))
  source("lib_helpers.R",local=environment()) 
  source("latex_code.R",local=environment())
  source("dataset/indices_and_factors/ff_industries_sic.R",local=environment())
  source("business_data_clean.R",local=environment())
  source("Paper_global_parameters.R",local=environment())
}

@@

#Add any/all choices made in the tool here
if(!exists("input") ){#& FALSE
  input = list()
  input$startdate <- as.Date("1984-12-31")
  input$enddate <- as.Date("2014-12-31")
  market_cap_min = "10"
  market_cap_max = "10000"
  quantile_used_ind = "0.2"
  quantile_used_all = "0.4"

@@

  input$characteristic_irats2 <- "pre.vol.Score"
  input$characteristic_irats2_sign <- T
}
market_cap_min = as.numeric(input$market_cap_min)
market_cap_max = as.numeric(input$market_cap_max)
quantile_used_ind = as.numeric(input$quantile_used_ind)
quantile_used_all = as.numeric(input$quantile_used_all)

#need to add environment here because this is called from Rmd
options(warn=-1) #because some period don't have data
source("report_helpers.R",local=environment()) 
source("report_tool.R",local=environment())
source("report_tool_section.R",local=environment())
options(warn=0)

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA_NEW$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of share authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
SEO_exit_days = sapply(which(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])
@

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
tmp = pnl_matrix(remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade))
ri = remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade)
expost_betas = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
ri = remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_12M,min_date=FirstTrade)
expost_betas_unhedged = beta_expost(ri,Risk_Factors_Monthly[,pnl_hedge_factors])
@

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all1mshort_risk_factors,min_date=FirstTrade))
months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all3mshort_risk_factors,min_date=FirstTrade))
months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all6mshort_risk_factors,min_date=FirstTrade))
months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade))
months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all24mshort_risk_factors,min_date=FirstTrade))
months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all36mshort_risk_factors,min_date=FirstTrade))
months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$long_all48mshort_risk_factors,min_date=FirstTrade))

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
EU_index_features = scrub(cbind(BUYBACK_DATA_NEW$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA_NEW$DATASET$SDC$pre_vol,BUYBACK_DATA_NEW$Valuation_Index))
colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
Under_IdioBB_cor = cor(EU_index_features)
@

@@

Figure~\ref{fig:Eundervaluationindex} shows the distribution of the EU-index. The index has a symmetric distribution with a mean of \Sexpr{round(mean(EUindex_bb),2)}. Table~\ref{tbl:EUrelations} shows how the EU-index relates to a number of firm characteristics. Firm leverage, based on data the year before announcement, is defined as the ratio $debt/(debt+equity)$\footnote{We use the definitions from \url{http://www.ivo-welch.info/professional/leverage.placebo/}{Ivo Welch's website} following  \url{http://www.ivo-welch.info/professional/leverage.placebo/r-sourcecode/mksane.R}. Debt is the sum of the Compustat variables $dlc+ dltt$, where $dlc$ is ``Debt in Current Liabilities'' and $dltt$ is ``Long Term Debt - Total''. Equity is the Compustat variable $seq$ which is ``Total Parent Stockholders' Equity''. We use the most recent data pre-announce, and make the winsorization and other adjustments as in the websites above. Note that we followed the same steps as in these websites to handle negative book value of equity (in the BE/ME calculations) and any other Compustat data issues.}. ``Missed (beat) EPS'' measures the percentage of firms in the specific EU index category that missed (beat) the last EPS consensus analyst forecast before the buyback announcement. ``ISS later'' measures the percentage of firms that announced an equity issue within 48 months after the buyback announcement. Next, we measure the percentage of buybacks financed with cash (CASH) when the data is available\footnote{As this SDC data was not available for many events, we did not consider the in the U-index calculation} (this data was available only for \Sexpr{sum(!(BUYBACK_DATA_NEW$DATASET$SDC$Source...of..Funds..Code == ""))} of the events) and whether the reported purpose (available only for \Sexpr{sum(!(BUYBACK_DATA_NEW$DATASET$SDC$Purpose.Code == ""))} events) included the term ``Undervalued'', or ``Enhance Shareholder Value'' or ``stock option plan''.

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp_market_cap = round(non_zero_mean(BUYBACK_DATA_NEW$DATASET$SDC$Market.Cap[EUindex_bb %in% c(4:6)])/1000,1)
@

First there is a striking negative relation between the EU index and financial leverage. This makes sense according to the static trade-off theory of optimal capital structure: high risky firms have more financial distress and should have less debt. Second, the high EU index firms are more likely to miss earnings forecasts. To the extent that analysts base their recommendations on these earnings misses, stock prices may become undervalued. Evidence that analyst extrapolation forecast errors are a partial explanation for the buyback anomaly is documented by \cite{PeyerVermaelen2009}.  High EU index firms are more likely to mention ``undervaluation'' as a motivation for the buyback.  High EU index firms tend to have more cash. This could of course be related to the fact that risky firms should have more cash holdings.  They also tend to follow up with equity offerings after the buyback which suggests that they are more likely to be in the ``market timing'' business. The table also shows a strong negative relation between market-to-book ratios and market capitalization and the EU index, which is not surprising as these are components of the index. It should be noted that the EU 6 portfolio is composed of very small stocks with an average market capitalization of \$\Sexpr{round(EU_relations["Market Cap.","EU6"],1)} million. The average market capitalization of portfolios with long term (after 48 months) monthly excess return of larger than 0.3$\%$ (i.e. portfolios EU4 through EU6 in Table~\ref{tbl:EUunderBBcal}) is \$\Sexpr{tmp_market_cap} billion (not indicated in the Table). So the buyback anomaly is to some extent a small cap anomaly, although portfolio EU3 for which the average market capitalization of its \Sexpr{sum(EUindex_bb==3)} firms is \$\Sexpr{round(non_zero_mean(BUYBACK_DATA_NEW$DATASET$SDC$Market.Cap[EUindex_bb ==3])/1000,1)} billion still has significant abnormal returns.

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
tmp = pnl_matrix(remove_initialization_time(High_EU_BB_Hedged,min_date=FirstTrade))
tmp1 = pnl_matrix(remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade))

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
latex_render_data_frame(
  pnl_matrix(remove_initialization_time(BUYBACK_DATA_NEW$long_all12mshort_risk_factors,min_date=FirstTrade)), 
  title = "Monthly and Yearly Five Factor Abnormal Rerurns of a strategy investing in all buybacks",
  caption="Monthly and yearly five-factor rolling hedged abnormal returns of an equally weighted (with monthly rebalancing) portfolio of all buybacks. The holding period for each buyback is 12 months per event.",
  label="tbl:allhedgedBB", 
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)
@

@@

number_eventsBB = table(format(BUYBACK_DATA_NEW$DATASET$SDC$Event.Date[BUYBACK_DATA_NEW$DATASET$SDC$Event.Date >= FirstTrade], "%Y"))
market_index = 100*(1+cumprod(1+Market_Monthly[names(Market_Monthly) >= "1985-01-01"]))
market_index = market_index[which(str_sub(names(market_index), start = 6, end = 7)=="12")]
names(market_index) <- str_sub(names(market_index), start = 1, end = 4)
df.bar <- barplot(number_eventsBB,col=c("grey"),main = "Panel A: Buyback Announcements", ylab = "Announcements", xlab = "Years",las=2,space=0.5, cex.names=0.6)
par(new = TRUE)
plot(market_index,type="l", lwd = 1.5, axes = FALSE, xlab = "", ylab = "")
points(market_index, pch=1,  lwd=1.5)
axis(side=4, at = pretty(range(market_index)))
mtext("Market Index", side=4, line=3)
for (iter in 1:floor(max(number_eventsBB)/100))
  abline(h = 100*iter)

@@

all_ret_values = data.frame(
  market = cumsum(100*Market_Monthly[str_sub(names(Market_Monthly), start = 1, end = 7) %in% str_sub(names(remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_1M,min_date=FirstTrade)), start = 1, end = 7)]),
  #market = cumsum(100*Market_Daily[names(remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_1M,min_date=FirstTrade))]),
  months1 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_1M,min_date=FirstTrade)),
  months3 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_3M,min_date=FirstTrade)),
  months6 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_6M,min_date=FirstTrade)),
  months12 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_12M,min_date=FirstTrade)),
  months24 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_24M,min_date=FirstTrade)),
  months36 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_36M,min_date=FirstTrade)),
  months48 = cumsum(100*remove_initialization_time(BUYBACK_DATA_NEW$pnl_returns_events_all_48M,min_date=FirstTrade))
)
plot(all_ret_values$market, axes=FALSE, ylab="Cumulative Returns", xlab = "Time",ylim=c(min(as.vector(all_ret_values)), max(as.vector(all_ret_values))), main = "Panel A: Absolute Returns", cex.lab=1.1, lty = "dotdash", type = "l", lwd=2)
axis(1,at=seq(1,nrow(all_ret_values),length.out=10),labels=str_sub(rownames(all_ret_values)[seq(1,nrow(all_ret_values),length.out=10)], start = 1, end=4),cex.axis=0.8,las=3)
axis(2,cex.axis=1.1)
lines(all_ret_values$months1, lty="solid", lwd=2)
lines(all_ret_values$months3, lty="dashed", lwd=2)
lines(all_ret_values$months6, lty="dotted", lwd=3)
lines(all_ret_values$months12, lty="dotted", lwd=2.5)
lines(all_ret_values$months24, lty="dotted", lwd=2)
lines(all_ret_values$months36, lty="dotted", lwd=1.5)
lines(all_ret_values$months48, lty="dotted", lwd=1)
for (iter in 1:floor(max(as.vector(all_ret_values))/100))
  abline(h = 100*iter)
#plot_crisis_dates(all_ret_values)
legend(x="topleft",
       c("S&P500","1 Month","3 Months","12 Months","24 Months","36 Months","48 Months"),
       lty=c("dotdash","solid","dashed","dotted","dotted","dotted","dotted","dotted"),
       lwd=c(2,2,2,3,2.5,2,1.5,1),
       cex=1,bg="white",inset=0.01)
